Atomify - a live LAMMPS visualizer

### 2017-05-07 ms.tex
Added flowchart

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{final_billboard.png}
	\caption{Workflow}
	\label{fig:gui}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{flowchart.png}
	\caption{The typical workflow when using LAMMPS. a) A LAMMPS script is written using a text editor. b) Simulation is performed from the terminal. c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}. Atomify simplifies the workflow by combining all steps into one application. }
	\label{fig:flowchart}
\end{figure}
